Individual and Differential Harm in Redistricting

### 2022-07-01 paper/paper.Rmd
re-run AL

This intuition is confirmed by a closer analysis, summarized in Figure \ref{fig:al-maps}(f).
Across the state, the estimated average harm is 0.082, which translates to around 161,000 voters.
Of these harmed voters, around 136,000 are Black, while 25,000 are White.
Similarly, 151,000 are Democratic, while only 10,000 are Republican.
Of course, the total number of each of these groups of voters is very different.
Normalizing by group sizes, the expected harm for a Black Democrat is 0.25, for a Black Republican is 0.015, for a White Democrat is 0.091, and for a White Republican is 0.0073.
Thus while the challenged plan differentially harms both Black voters and Democratic voters, it *especially* harms Black Democrats, who have a differential harm of 0.158 versus White Democrats and a differential harm of 0.235 versus Black Republicans.

@@

The mean support $\mu^{(s)}$ receives an informative prior based on the racially polarized voting estimates of @kuriwaki2021geography, with $\mu^{(s)}\sim\Norm(\logit((0.18, 0.90, 0.35)), (0.04^2, 0.04^2, 0.2^2))$.
These estimates were derived through multilevel regression and poststratification from survey data, calibrated to actual election results.

>>>>

This intuition is confirmed by a closer analysis, summarized in Figure \ref{fig:al-maps}(f).
Across the state, the estimated average harm is 0.079, which translates to around 159,000 voters.
Of these harmed voters, around 123,000 are Black, while 36,000 are White.
Similarly, 137,000 are Democratic, while only 22,000 are Republican.
Of course, the total number of each of these groups of voters is very different.
Normalizing by group sizes, the expected harm for a Black Democrat is 0.22, for a Black Republican is 0.037, for a White Democrat is 0.083, and for a White Republican is 0.017.
Thus while the challenged plan differentially harms both Black voters and Democratic voters, it *especially* harms Black Democrats, who have a differential harm of 0.138 versus White Democrats and a differential harm of 0.183 versus Black Republicans.

@@

The mean support $\mu^{(s)}$ receives an informative prior based on the racially polarized voting estimates of @kuriwaki2021geography, with $\mu^{(s)}\sim\Norm(\logit((0.18, 0.90, 0.35)), (0.03^2, 0.03^2, 0.2^2))$.
These estimates were derived through multilevel regression and poststratification from survey data, calibrated to actual election results.
